A Toolbox for Manipulating and Assessing Color Palettes for Statistical Graphics

### 2019-02-19 pkg/colorspace/paper/Toolbox/slides.Rnw
added recommendation slide
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@449 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{colorspace}

@@

>>>>

\section{colorspace: A Toolbox for Manipulating and Assessing Color Palettes for Statistical Graphics}

@@

\subsection{Recommendations}

\begin{frame}
\frametitle{Recommendations}

\begin{itemize}
  \item Do not overestimate the effectiveness of color.
  \item Choose type of palette based on the data to be visualized.
  \item For areas use light colors (higher luminance, lower chroma).
  \item For points/lines darker colors are needed (lower luminance, higher chroma).
  \item For palettes with more colors stronger luminance contrasts are needed.
  \item Triangular chroma trajectories useful for distinguishing central colors.
\end{itemize}
